The Regional Effects of Marine Protected Areas

### 2020-04-26 README.Rmd
resubmissted version to PNAS (#1)
* version re-submited to PNAS

>> Marine Protected Areas (MPAs) cover between 3-7% of the world's oceans, up from less than 1% in the year 2000. The Convention on Biological Diversity calls for 10% of coastal waters to be protected inside MPAs by 2020, while the International Union for Conservation of Nature calls for 30% protection by 2030. It is often clear that MPAs produce conservation benefits inside their borders, but many MPAs are also justified on the grounds that they also benefit the broader region outside their borders. Despite the expanding role of MPAs in marine resource management, we lack a clear understanding of what the regional effects of MPAs might be, and how we might detect them in scientific studies. We used a bio-economic simulation model to demonstrate how the regional effects of MPAs are affected by a suite of economic and environmental drivers and show how commonly used methods to measure inside-MPA effects are likely to fail to capture the regional impacts of protection. We present an empirical strategy for estimating regional MPA effects on biomass density using 16 years of data from inside and outside of MPAs within the Channel Islands, California, USA. We find no statistically clear effect of MPAs on aggregate mean biomass densities of targeted finfish throughout the study region. To make meaningful progress on MPA design and evaluation, the next generation of MPA science must address the challenge of understanding and estimating the regional effects of MPAs across the diversity of species in the ecosystem.

>>>>

>>  Marine Protected Areas (MPAs) cover 3-7% of the world’s ocean, up from less than 1% in the year 2000, and international commitments call for 10%, 30%, and even 50% coverage. The premise underlying MPA expansion is that they conserve biodiversity, habitats, and fished populations. While numerous studies show that MPAs produce conservation benefits *inside* their borders, many MPAs are also justified on the grounds that they confer conservation benefits to the broader population *beyond* their borders. This paper examines the conditions under which MPAs can provide population-level conservation benefits inside and outside their borders, and shows that even in cases when the conservation benefits are large, they are inherently difficult to detect empirically. A network of MPAs was put in place in The Channel Islands National Marine Sanctuary in 2003, with a goal of providing regional conservation and fishery benefits. Evidence indicates that the Channel Island MPAs have increased biomass densities inside the MPAs, but we are unable to find a clear effect of these same MPAs at the population level. MPA effect sizes less than 30% are likely to be difficult to detect (even when they are present), and the size of many MPA networks suggests that effect sizes may often be smaller than 30%. Our results provide a novel assessment of the population-wide effects of a large and iconic Marine Protected Area network, and provide guidance for communities charged with monitoring and adapting MPAs.

### 2020-04-26 documents/cover-letter.Rmd
resubmissted version to PNAS (#1)
* version re-submited to PNAS

##

@@

White, J. W., Botsford, L. W., Baskett, M. L., Barnett, L. A., Barr, R. J. and Hastings, A. (2011), Linking models with monitoring data for assessing performance of no‐take marine reserves. Frontiers in Ecology and the Environment, 9: 390-399. doi:10.1890/100138

Burgess, S. C., Nickols, K. J., Griesemer, C. D., Barnett, L. A., Dedrick, A. G., Satterthwaite, E. V., Yamane, L. , Morgan, S. G., White, J. W. and Botsford, L. W. (2014), Beyond connectivity: how empirical methods can quantify population persistence to improve marine protected‐area design. Ecological Applications, 24: 257-270. doi:10.1890/13-0710.1

Smith, M. D., & Wilen, J. E. (2003). Economic impacts of marine reserves: the importance of spatial behavior. Journal of Environmental Economics and Management, 46(2), 183-206. doi:https://doi.org/10.1016/S0095-0696(03)00024-X

Smith, M. D., Zhang, J., & Coleman, F. C. (2006). Effectiveness of marine reserves for large-scale fisheries management. Canadian Journal of Fisheries and Aquatic Sciences, 63(1), 153-164. doi:10.1139/f05-205

Kaplan, K. A., L. Yamane, L. W. Botsford, M. L. Baskett, A. Hastings, S. Worden, and J. W. White. 2019. Setting expected timelines of fished population recovery for the adaptive management of a marine protected area network. Ecological Applications 29(6):e01949. 10.1002/eap.1949

>>>>

# Responses

We thank the two reviewers and the Editor for their constructive responses. We have fundamentally restructured the paper to place much greater emphasis on the empirical results from the Channel Islands MPA network. This is to our knowledge the first empirical assessment of the regional effects of a large and iconic MPA network on a wide assemblage of commercially and economically important species. Our inability to estimate a clear effect in such a well-enforced and well-studied local is we feel a vitally important "null-result" both for scientists and MPA managers to be aware of. As such we feel that it warrants publication in PNAS. While our results are more focused on the empirical results, we explicitly link our results to the large body of MPA theoretical work, using it to help illustrate why we might expect such a null result and help managers understand when they might be able to detect an effect. As MPAs are used as a core tool of marine resource management, our results provide a critical update to our empirical expectations for MPAs, that to date have been based almost entirely on inside-outside MPA response ratios. We hope you find the updated version of our manuscript improved thanks to the inclusions of the careful points raised by the prior revision of this paper.

## Reviewer 1

- *I think that greater emphasis needs to be placed up front, abstract, statement of significance, introduction..perhaps even title, that this model and paper only addresses fish biomass...not other 'conservation outcomes'. You do define this but not until page 2, line 148-154. I recommend moving this up.*
  - We apologize for not making this clearer in our earlier draft, and have included this key caveat in the abstract, statement of significance, and introduction (Line 98)

- *I was surprised that there was no discussion about enforcement being a potential confounding factor. Currently the paper assumes that the Channel Islands MPAs are fully enforced, without poaching. This may or may not be the case and should be stated as such. You do address well other system wide impacts like water temperature (lines 557-8, 691+). Perhaps enforcement could be added to the discussion around line 711-13.*
  - This is indeed a critical point that we have endeavored to correct. We have included enforcement under our summary of key enabling conditions for effective MPAs (line 124), as well as the discussion (line 382). While we do not have published data on strength of enforcement within the MPAs, anecdotal evidence suggests it is relatively high, as well as evidence from the mainland California MPAs (Zellmer et al. 2018) indicates it is high. In addition, the presence of a clear increase in response ratios within the Channel Islands provides evidence that the MPAs  are large enough and sufficiently well-enforced as to provide meaningful protection within their borders (Line XX).

- *Your discussion of the model also emphasizes that stock status prior to MPA designation is very key to outcomes; in the SI most of the species included for the Channel Island review have unknown status---which influences your discussion, and may better be described.*
  - We make clearer that we iterate over unknowns such as pre-MPA stock status in our description of the Channel Islands simulations (line XX), and the implications of pre-MPA stock status in the discussion (Line XX).

## Reviewer 2

- *Yes, these are important questions but they are not new to ecology, economics, and fishery science. You are not the first to ask them and point out their importance; see articles at bottom for some examples. What are you doing to answer them that is better than all of the other papers that come before you? And why is your case study an exemplary place to answer the questions? The conclusions on line 709-728 are well-known in the MPA literature.*
  - We have fundamentally restructured the paper based around the importance of the Channel Islands as a case study in measuring MPA effectiveness. We thank the reviewer for pointing out gaps in our literature, and we have incorporated the studies they recommend. The theoretical points we raise have indeed been pointed out in the literature before, and we feel our new manuscript makes that clearer. The Channel Islands MPAs are an iconic network that has served as a model for protected areas around the world. It is also incredibly well-studied and well-enforced. While previous studies have looked the effectiveness of the Channel Islands MPAs within their borders, this is the first study in the Islands (and globally of which we are aware) to attempt an estimate of the effect of the MPAs at the regional scale (both inside and outside of the MPAs themselves). That we are unable to estimate a clear regional effect in even this system is an important result that we feel warrants publication in PNAS. As MPAs are increasingly turned to tools for ocean conservation, our results provide an important update and caution to expectations based solely on inside-outside comparison studies.

- *I would also be more cautious regarding your conclusion about your model predicts what should be expected in the data analysis. It could be simply luck that there is agreement between the two.*
  - We have made the language clearer that this concordance could be simple coincidence, and is not in any way proof of the validity of our results (Line XX) However, in light of recent concerns in the scientific literature around hypothesizing-after-results, we feel that it is critically important to ground our theoretical results in *a priori* predictions. In addition, as we mention in the discussion, we encourage MPA scientists and stakeholders to undertake such simulation modeling to consider the plausibility of their results. As the reviewer says, empirical results that match theoretical predictions are not proof that the empirical methods are robust, but they do provide am additional and important line of evidence: empirical results that fail to match theoretical predictions need to be carefully considered.

- *What about using the simulation model to demonstrate the validity of the technique used to identify the MPA effect used in the paper, which was pioneered in publication in 38? Or to understand whether the implication of the statement on line 539, that is, species ranges exceed the Island and your sampling domain, is important for measuring the impacts of MPAs outside of their boundaries? In sum, in its current form, I would move all of the simulation model to the SI (lines 131-252) and mention in the discussion section that these results are consistent with the predictions of a stylized single species model.*
    - We have greatly expanded the simulation validation of our method, which was previously included in the supplementary material. Figure 4 of the paper now demonstrates the validity (and shortcomings) of the model under a variety of plausible conditions. We would note that this method is related to that described in Caselle et al. 2015 (previously reference #38), but is not the same. Our method explicitly estimates the net difference in the targeted and non-targeted biomass densities pre-and-post MPA as an estimate of the mean effect of the MPAs  both inside and outside their borders. Caselle et al. 2015 used trends in targeted and non-targeted species inside and outside of MPAs to illustrate the effects of the MPAs within their borders. We stress this difference in an effort to make clear that our results and methods are not simply an update to Caselle et al. 2015, but address a fundamentally different question. We hope we have made this clearer in the text, e.g. on line XX.

    With regards to the specific question about the possibility of the species range exceeding the sampling domain, this would be reflected as a reduction in the percent of the population protected by the MPAs: a 25km^2 MPA may provide near total protection for a sedentary species with brood-rearing, but be insignificant to a migratory tuna. To that end, our assessment of model performance as a function of MPA effect size addresses the question of hwo MPA size relative to species range affects our models performance. All else being equal the smaller a portion of a population's range is protected by MPAs, the smaller the expected effect size, and by extension the more challenge the estimation model will have.

  We apologize that we did not present our prior simulation work in a sufficiently compelling manner, and failed to differentiate its results from the prior literature. As suggested by the reviewers and the editor, we have restructured the paper to place much greater emphasis on the critical results from the Channel Islands. However, we feel that the simulation results do provide vital context to our results, and provide tangible recommendations as to under what circumstances we might be able to estimate the regional effects of MPAs. The reviewer correctly points out that the individual components of our model are not themselves novel, and that the importance of fleet dynamics and fish dispersal have been previously discussed. As such as have greatly reduced the attention these results receive, except as a vehicle for the explicit consideration of the feasibility of estiamting reginoal MPA effects. In addition, while these broad points have been made in the literature before, we feel there is value in cohesively demonstrating the ramifications of these diverse pieces of MPA theory (that generally are looked at only one or a few at a time) in once place, both through our Figure 5 and the accompanying web application. We hope that these modifications make clear the contribution of the simulation modeling.

- *The discussion on how to detect changes outside the MPA (lines 254-347) follows very closely the discussion in Ferraro et al (#41 in your list). It seems like you can remove most of this text and point the reader to that paper*
  - We have greatly reduced the amount of text addressing response ratios, and restructured the response-ratio analysis to be linked explicitly with the empirical response ratios observed in the Channel Islands (in response to comments from the editor), in Figure 1. We feel this strategy makes much clearer how the results of this paper expand beyond the findings of Caselle et al. 2015, and why the results of Caselle et al. 2015 are evidence of within-MPA effects, but not of the question of regional effects addressed in this manuscript. Given that much of the MPA literature relies on response ratios as the empirical evidence for the effectiveness of MPAs, we feel that it is critically important to directly address the challenges of response ratios as measures of regional effects in this paper. We hope that the new manner, directly linking theoretical response ratios to the levels observed in the Channel Islands.

- *To me the potential contribution of the paper starts on line 350, which is way too late in a paper of this size*
  - We have restructured the paper so that it now focuses on the Channel Islands case study, and as suggested have moved this discussion up to the introduction (line 97).

- *Is part of assumption b) (line 372) that the dispersal characteristics of the fished and non-fished species need to be similar? I could envision a scenario where the two sets of species have different dispersal characteristics, non-fished have smaller dispersal ranges than fished species, for example. How does this impact your identification strategy? If the trends are similar regardless of the mechanistic process by which it occurs, does it matter for the empirics? More discussion on both assumptions (a) and (b) and what they imply about the biological mechanisms seems warranted.*
  - The estimation model does not depend on the dispersal characteristics of the fished and non-fished species per-say. The model is operating at the level of biomass densities. As such, even if a non-targeted species has a much bigger range than the targeted species (or even the sampling region), so long as the parallel trends assumption holds within the sampled portion of the non-targeted species range, the identification strategy may be valid. Similarly, the model is agnostic as to the root causes of the parallel trends, so long as they exist. However, if for example the parallel trends are dependent on a particular temperature regime which during the study is disrupted (as is likely the case in our data), then the model may be reliable for the early years but not later. We have made this point clearer in the paper (line XX), and made clear that the lack of a clear effect in the recent years is likely due to an emerging violation of the parallel trends assumption, and not to a failure of the MPAs per say. However, this is still an important result, since it suggests that neither the response ratios nor the difference-in-difference method give us a robust estimate of the regional effects of the Channel Island MPAs. As we stress in the paper, that even in a network such as the Channel Islands we ar left without a clear empirical effect at the regional level has critical ramificaitons for the design and monitoring of MPAs globally.

- *The use of visual data surveys has, of course, problems that introduce errors in dependent and independent variables that could be correlated with features of the fished and non-fished species, e.g., size distribution. How can you be sure that this is not driving your results? Could you use the simulation model to investigate this?*
  - Visual survey data are indeed challenging, but also often the only form of data available for MPA analysis. Our base model operates at the level of total biomass density of targeted and non-targeted species, at the site level. This is the finest spatial scale at which the sampling regime would be likely to provide an estimate of the variable in question, since while any individual transect is unlikely to observe all of the targeted / non-targeted, but aggregating across transects provides a better chance of this. These totals are derived from average biomass densities of indivudal species across multiple transects within each site, which are then summed across species to achieve the total mean biomass density at the site level. The averaging process in acts to smooth out some of the sampling variation, and reflects a broader discussion about the right degree of smoothing in spatio-temporal data.

How might this affect our results? So long as sampling errors are consistent over time, they should not bias the mean or the trends of our results (e.g. if we systemically under/over estimate the biomass of some species). There is no doubt though that we are underestimating the true magnitude of the credible intervals though. For example, the model assumes constant length-to-weight relationships over time, whereas in reality there is clearly variation both among individuals and over time. Accounting for this should add more noise to our data, further complicating the ability of our model to achieve precise estimates. Complicated relationshops such as the MPAs themselves affecting the length-to-weight relationship would indeed skew our results, but we feel that is beyond the scope of this or any other MPA study of which we are aware to address.

  We have run our model at a wide array of resolutions, from the updated aggregated form we use here to a complete hierarchical framework that attempts to control for errors in the individual observation process (Fig.SXX). The fundamental results remains the same: a general upwards trend, followed by a downward trend, with the clearest signal in the years around 2010. We would actually be more concerned about the robustness of our results if we had found a precise but small effect size: such an effect could easily dissapear if we accounted for errors in the data (e.g. through allowing for variations in the length-weight relationship). Our relatively uncertain findings instead suggests that it is unlikely that we would get fundamentally different conclusions by including more error; we would simply be even less certain than the uncertain state the model estiamtes we are in. We have expanded the simulation testing of the method a bit to help illustrate how violations of the model assumptions play out, and how they are related to the magnitude of the effect size (Figure 5). The full suite of alternative resolution models can be found in Figs.SXX-XX (all of which show the same general result), and a a simulation test of our model incorporating factors such as differing diver skill can be found in Fig.SXX (which shows that the model is capable of performign under such circumstances).

- *(The answer to your question on line 709 that appears on lines 714-719 has been known in the literature on MPAs for over 20 years; see, e.g., papers by Martin Smith below. Given that your question is what "your results imply about the future of marine science", my answer is not very much. Again, you did a rigorous empirical case study that should be published. I am however finding it difficult to see a path to publication in PNAS.)*
  - We hope that our restructuring around the novel empirical results resolves this concern. While we agree that framing our results around the future of marine science would be a step too far, we would point out that our earlier and present draft asked what our results imply for the future of MPA science more specifically, which we hope is less of a stretch.

  Given the increasing role of MPAs in conservation strategies, the lack of a clear regional effect in a place like the Channel Islands should be known and taken into account by MPA practitioners around the globe. We agree that we framed our simulation results poorly in previous drafts, but feel that they do compliment the empirical results to help managers understand why the Channel Islands results may not be surprising, and when they might expect to be able to detect and effect, and when not. See section 2.1.2 ("When can we detect the effects of MPAs") and our updated conclusions, in particular the paragraph beginning on line XX.

- *Examples of relevant literature, you should expand your net to find other relevant literature to better distinguish your contribution*
  - We thank the reviewer for pointing out these important omissions, in particular @white2011, @smith2006, @nickols2019. We have included each of these references in their appropriate portions of the paper

## Editor

# Original Reviews

@@

*White, J. W., Botsford, L. W., Baskett, M. L., Barnett, L. A., Barr, R. J. and Hastings, A. (2011), Linking models with monitoring data for assessing performance of no‐take marine reserves. Frontiers in Ecology and the Environment, 9: 390-399. doi:10.1890/100138*

*Burgess, S. C., Nickols, K. J., Griesemer, C. D., Barnett, L. A., Dedrick, A. G., Satterthwaite, E. V., Yamane, L. , Morgan, S. G., White, J. W. and Botsford, L. W. (2014), Beyond connectivity: how empirical methods can quantify population persistence to improve marine protected‐area design. Ecological Applications, 24: 257-270. doi:10.1890/13-0710.1*

*Smith, M. D., & Wilen, J. E. (2003). Economic impacts of marine reserves: the importance of spatial behavior. Journal of Environmental Economics and Management, 46(2), 183-206. doi:https://doi.org/10.1016/S0095-0696(03)00024-X*

*Smith, M. D., Zhang, J., & Coleman, F. C. (2006). Effectiveness of marine reserves for large-scale fisheries management. Canadian Journal of Fisheries and Aquatic Sciences, 63(1), 153-164. doi:10.1139/f05-205*

*Kaplan, K. A., L. Yamane, L. W. Botsford, M. L. Baskett, A. Hastings, S. Worden, and J. W. White. 2019. Setting expected timelines of fished population recovery for the adaptive management of a marine protected area network. Ecological Applications 29(6):e01949. 10.1002/eap.1949*

# References

### 2020-04-26 documents/ovando-regional-effects-of-mpas-nopnas.Rmd
resubmissted version to PNAS (#1)
* version re-submited to PNAS

---
title: The Regional Effects of Marine Protected Areas
author:
  - name: Daniel Ovando
    affiliation: a,1
    email: danovan@uw.edu
  - name: Jennifer E. Caselle
    affiliation: b
  - name: Christopher Costello
    affiliation: b   
  - name: Olivier Deschenes
    affiliation: b  
  - name: Steven D. Gaines
    affiliation: b
  - name: Ray Hilborn
    affiliation: a
  - name: Owen Liu
    affiliation: b        
address:
  - code: a
    address: University of Washington, School of Aquatic and Fishery Sciences
  - code: b
    address: University of California, Santa Barbara
corresponding_author:
  - code: 1
    text: "To whom correspondence should be addressed. E-mail: danovan@uw.edu"
lead_author_surname: Ovando
author_contributions: |
  D.O., S.G., and R.H. developed structure of simulation model. D.O., O.D., C.C., and J.C. developed estimation strategy. J.C. provided support on collecting and interpreting data. All simulations, statistics, and sensitivity analyses performed by D.O. and O.L. . All authors contributed to the manuscript. 
conflict_of_interest: |
  R.H's research program receives funding from environmental NGOs, foundations, fishing industry, governments and international agencies. All of these can be interpreted as a conflict of interest when evaluating fisheries policy. C.C., S.G., and O.D's research program includes funding from environmental NGOs and foundations with an interest in ocean conservation and food security. Funding for D.O. was partly provided by the NMFS-Sea Grant Population and Ecosystem Dynamics Fellowship.
abstract: |
  Marine Protected Areas (MPAs) cover between 3-7% of the world's oceans, up from less than 1% in the year 2000. The Convention on Biological Diversity calls for 10% of coastal waters to be protected inside MPAs by 2020, while the International Union for Conservation of Nature calls for 30% protection by 2030. It is often clear that MPAs produce conservation benefits inside their borders, but many MPAs are also justified on the grounds that they also benefit the broader region outside their borders. Despite the expanding role of MPAs in marine resource management, we lack a clear understanding of what the regional effects of MPAs might be, and how we might detect them in scientific studies. We used a bio-economic simulation model to demonstrate how the regional effects of MPAs are affected by a suite of economic and environmental drivers and show how commonly used methods to measure inside-MPA effects are likely to fail to capture the regional impacts of protection. We present an empirical strategy for estimating regional MPA effects on biomass density using 16 years of data from inside and outside of MPAs within the Channel Islands, California, USA. We find no statistically clear effect of MPAs on aggregate mean biomass densities of targeted finfish throughout the study region. To make meaningful progress on MPA design and evaluation, the next generation of MPA science must address the challenge of understanding and estimating the regional effects of MPAs across the diversity of species in the ecosystem.
significance: |
acknowledgements: |
keywords:
  - Marine Protected Areas
  - Conservation
  - Bio-economic modeling
  - Program Evaluation
## must be one of: pnasresearcharticle (usual two-column layout), pnasmathematics (one column layout), or pnasinvited (invited submissions only)
pnas_type: pnasresearcharticle
bibliography: My Library.bib
csl: pnas.csl
lineno: true
header-includes:
   - \usepackage{eso-pic,graphicx,transparent,xcolor}
output:
  rticles::pnas_article: default
  bookdown::word_document2: default
  bookdown::pdf_document2: default
  bookdown::html_document2: default
params:
  run_name: ["v5.0"]
  sim_years: [50]
  burn_years: [20]
  num_patches: [25]
linkcolor: blue
---

@@

\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: danovan@uw.edu}

<!-- \AddToShipoutPictureFG{ -->
<!--   \AtPageCenter{% or \AtTextCenter -->
<!--     \makebox[0pt]{\rotatebox[origin=c]{45}{% -->
<!--       \scalebox{5}{\texttransparent{0.3}{DRAFT}}% -->
<!--     }} -->
<!--   } -->
<!-- } -->

@@

Indeed, many recent agreements to expand MPAs (most proximately, the Convention on Biological Diversity’s Strategic Plan for Biodiversity, which calls for 10% of coastal waters to be protected inside MPAs by 2020 and the International Union for Conservation of Nature call for 30% by 2030) rely on the belief that well-designed MPAs will achieve benefits both within, and outside, their borders. Despite these assumptions, our collective scientific understanding of the regional-scale conservation and fishery impacts of current and future MPAs is surprisingly limited.

@@

<!-- \showmatmethods -->
\showacknow

&nbsp;
&nbsp;
&nbsp;

>>>>

---
title: The Regional Effects of Marine Protected Areas
author: Daniel Ovando, Jennifer E. Caselle, Christopher Costello, Olivier Deschenes, Steven D. Gaines, Ray Hilborn, and Owen Liu    
date: "Document compiled on `r Sys.Date()`"
bibliography: My Library.bib
header-includes:
   - \usepackage{eso-pic,graphicx,transparent,lineno}
   - \linenumbers
output:
  bookdown::pdf_document2: default
  bookdown::word_document2: default
  bookdown::html_document2: default
params:
  run_name: ["v5.0"]
  sim_years: [50]
  burn_years: [20]
  num_patches: [25]
---

@@

\AddToShipoutPictureFG{
  \AtPageCenter{% or \AtTextCenter
    \makebox[0pt]{\rotatebox[origin=c]{45}{%
      \scalebox{5}{\texttransparent{0.3}{DRAFT}}%
    }}
  }
}

# Abstract

Marine Protected Areas (MPAs) cover between 3-7\% of the world's oceans, up from less than 1% in the year 2000. The Convention on Biological Diversity calls for 10% of coastal waters to be protected inside MPAs by 2020, while the International Union for Conservation of Nature calls for 30\% protection by 2030. It is often clear that MPAs produce conservation benefits inside their borders, but many MPAs are also justified on the grounds that they also benefit the broader region outside their borders. Despite the expanding role of MPAs in marine resource management, we lack a clear understanding of what the regional effects of MPAs might be, and how we might detect them in scientific studies. We used a bio-economic simulation model to demonstrate how the regional effects of MPAs are affected by a suite of economic and environmental drivers and show how commonly used methods to measure inside-MPA effects are likely to fail to capture the regional impacts of protection. We present an empirical strategy for estimating regional MPA effects on biomass density using 16 years of data from inside and outside of MPAs within the Channel Islands, California, USA. We find no statistically clear effect of MPAs on aggregate mean biomass densities of targeted finfish throughout the study region. To make meaningful progress on MPA design and evaluation, the next generation of MPA science must address the challenge of understanding and estimating the regional effects of MPAs across the diversity of species in the ecosystem.

# Significance

# Main Body

@@

Indeed, many recent agreements to expand MPAs (most proximately, the Convention on Biological Diversity’s Strategic Plan for Biodiversity, which calls for 10\% of coastal waters to be protected inside MPAs by 2020 and the International Union for Conservation of Nature call for 30\% by 2030) rely on the belief that well-designed MPAs will achieve benefits both within, and outside, their borders. Despite these assumptions, our collective scientific understanding of the regional-scale conservation and fishery impacts of current and future MPAs is surprisingly limited.

@@

# Acknowledgements
